Conjure: Summoning Proxies from Unused Address Space

### 2019-11-22 paper/figures.tex

\newcommand{\FigUpload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-up.pdf}
    \caption{\textbf{Upload Performance}\,---\,\rm%
        We used iperf to measure the upload bandwidth for a direct connection, TapDance, and \scheme.
        As expected, TapDance's upload performance is several orders of magnitude lower than
        the link capacity, due to the overhead of frequent reconnects to the decoy.
    }
    \label{fig:upload}
\end{figure}
}

\newcommand{\FigDownload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-down.pdf}
    \caption{\textbf{Download Performance}\,---\,\rm%
        Using iperf, we compare the download performance of a direct connection, TapDance, and \scheme.
        While TapDance can achieve link capacity download, it still has to occasionally reconnect
        to the decoy, as seen by the periodic dips. These reconnects are more common the more data
        the client sends (e.g. requests or any upload data).
    }
    \label{fig:download}
\end{figure}
}

@@

\newcommand{\FigTapBandwidth}{
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.75\linewidth,clip]{figures/decoy-tap-bandwidth.png}
    \caption{\textbf{Tap Bandwidth}\,---\,\rm%
        We deployed our \scheme implementation in a realistic ISP testbed on a
        tap of a 20~Gbps router. As shown in a typical week, traffic
        ranges from 2-17~Gbps.
    }
    \label{fig:tap-bandwidth}
\end{figure*}
}

\newcommand{\FigIpEntropy}{
\begin{figure}[t]
    \centering
    %\includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
    \includegraphics[width=\linewidth,clip]{figures/entropy-ip-16hr.png}
    \caption{\textbf{IPv6 Entropy}\,---\,\rm%
        Censors may be able to distinguish random-looking phantom host IPv6 addresses
        from legitimately used ones based on the address's entropy.
        We used the Entropy/IP tool~\cite{foremski2016entropy} to analyze the entropy
        of 4013 IPv6 addresses observed by our tap. This plot from the tool shows the
        normalized entropy of each nibble in the addresses, which is fairly high
        for most of the non-network prefix nibbles. In total, these addresses have
        about 75~bits of entropy (out of 96 expected), and the relatively high entropy
        present in each nibble would make it difficult for a censor to block without
        significant false positives / negatives. While distinguishable from random
        given enough samples,
        we can also use the Entropy/IP tool to generate addresses from the Bayesian Network
        model it produces.}
    \label{fig:ipentropy}
\end{figure}
}

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \caption{\textbf{IPv6 bits set}\,---\,\rm%
        We measure the number of bits set to 1 in IPv6 addresses in our ISP's /32
        and observed by our tap,
        and compare it to the Binomial distribution (Random) we would expect to see
        if the 96 non-network bits of each address were chosen randomly. In practice,
        we observe much fewer bits set.
        Nonetheless, the significant overlap of these distributions
        would make it difficult for censors to block any individual phantom hosts
        without collateral risk of blocking legitimate services.
       % suggesting that censors might be able to distinguish between phantom host addresses
        % and legitimate ones.
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym.\ routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resistant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %ISP Deployment           &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \medskip
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,\rm%
        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
        without needing an inline element in the ISP network.
        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
        the protocol.
        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
        or upload arbitrarily large content.}
    \label{tab:compare}
\end{table*}
}

>>>>

\newcommand{\FigUpload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-up.pdf}\vspace{-2pt}
    \caption{\textbf{Upload Performance}\,---\,\rm%
        We used iperf to measure the upload bandwidth for a direct connection, TapDance, and \scheme.
        As expected, TapDance's upload performance is several orders of magnitude lower than
        the link capacity, due to the overhead of making frequent reconnects to the decoy site.
    }
    \label{fig:upload}
\end{figure}
}

\newcommand{\FigDownload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-down.pdf}\vspace{-2pt}
    \caption{\textbf{Download Performance}\,---\,\rm%
        Using iperf, we compare the download performance of a direct connection, TapDance, and \scheme.
        While TapDance can achieve link-capacity download, it still has to occasionally reconnect
        to the decoy, as seen by the periodic dips. These reconnects are more common the more data
        the client sends (e.g. requests or uploads).
    }
    \label{fig:download}
\end{figure}
}

@@

\newcommand{\FigTapBandwidth}{
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.75\linewidth,clip]{figures/decoy-tap-bandwidth.png}
    \caption{\textbf{Tap Bandwidth}\,---\,\rm%
        We deployed \scheme in a realistic ISP testbed on a
        tap of a 20~Gbps router. In a typical week, traffic
        ranges from 2--17~Gbps.
    }
    \label{fig:tap-bandwidth}
\end{figure*}
}

\newcommand{\FigIpEntropy}{
\begin{figure}[t]
    \centering
    %\includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
    \includegraphics[width=0.95\linewidth,clip]{figures/entropy-ip-16hr.png}
    \caption{\textbf{IPv6 Entropy}\,---\,\rm%
        Censors may be able to distinguish random-looking phantom host IPv6 addresses
        from legitimately used ones based on the address's entropy.
        We used the Entropy/IP tool~\cite{foremski2016entropy} to analyze the entropy
        of 4013 IPv6 addresses observed by our tap. This plot from the tool shows the
        normalized entropy of each nibble in the addresses, which is fairly high
        for most of the non-network prefix nibbles. In total, these addresses have
        about 75~bits of entropy (out of 96 expected), and the relatively high entropy
        present in each nibble would make it difficult for a censor to block without
        significant false positives / negatives. While distinguishable from random
        given enough samples,
        we can also use the Entropy/IP tool to generate addresses from the Bayesian Network
        model it produces.\vspace{-5pt}}
    \label{fig:ipentropy}
\end{figure}
}

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \caption{\textbf{IPv6 Bits Set}\,---\,\rm%
        We measure the number of bits set to 1 in IPv6 addresses in our ISP's /32
        and observed by our tap,
        and compare it to the Binomial distribution (Random) we would expect to see
        if the 96 non-network bits of each address were chosen randomly. In practice,
        we observe much fewer bits set.
        Nonetheless, the significant overlap of these distributions
        would make it difficult for censors to block any individual phantom hosts
        without collateral risk of blocking legitimate services.
       % suggesting that censors might be able to distinguish between phantom host addresses
        % and legitimate ones.
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym.\ routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resistant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %ISP Deployment           &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \medskip
    \caption{\textbf{Comparing Refraction Networking Schemes}\,---\,\rm%
        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
        without needing an inline element in the ISP network.
        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
        the protocol.
        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
        or upload arbitrarily large content.\vspace{-10pt}}
    \label{tab:compare}
\end{table*}
}

### 2019-11-22 paper/related.tex
minor edits from Nikita

TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30-120 seconds), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. \scheme addresses this issue and allows
clients to maintain long-lived connections to the phantom host.

@@

\subsection{Decoy Placement and Routing Attacks}

>>>>

TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30--120\,s), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. \scheme addresses this issue and allows
clients to maintain long-lived connections to the phantom host.
\looseness=-1

@@

\subsection{Decoy Placement and Routing Attacks}
\label{sec:placement-rad}
